Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-14 paper/paper.qmd
Made model validation with RMSE more explicit in intro and fixed RMSE naming in model section

For the remainder of the paper, the data section (@sec-data) goes over the data we used and its features and limitations, how the data was obtained, our variables of interest for our model and preliminary analysis, and a bit of our data cleaning process. The model section (@sec-model) discusses the type of model we used, the relationships between variables in our model, and the justification for our model. The results section (@sec-results) contains tables and graphs created based on our data and the results from our model. The discussion section (@sec-discussion) goes over what we did in our results, explaining the meaning of our findings, the implications of our findings to the real world, and areas of improvement and suggestions for future works. The appendix (@sec-appendix) includes a link to a dashboard that was created with interactive versions of the graphs in this paper, additional tables, notes on reproducing and code styling, model diagnostics and validation, our idealized survey and methodology to gather data on investigators responsible for homicide cases, and our evaluation of The Washington Post's methodology.

@@

Performing root mean square deviation (RSME) calculations on our model in @tbl-model-result yields a RSME value of about 0.45. RSME represents the difference between the model's predicted values and observed values with 0 meaning that the predicted and observed values are the same [@citejim]. Since the model's RSME value is close to 0, we can say our model is able to predict values with less error compared to other models that have a higher RSME value.

>>>>

For the remainder of the paper, the data section (@sec-data) goes over the data we used and its features and limitations, how the data was obtained, our variables of interest for our model and preliminary analysis, and a bit of our data cleaning process. The model section (@sec-model) discusses the type of model we used, the relationships between variables in our model, the justification for our model including the root mean square error (RMSE) for our model. The results section (@sec-results) contains tables and graphs created based on our data and the results from our model. The discussion section (@sec-discussion) goes over what we did in our results, explaining the meaning of our findings, the implications of our findings to the real world, and areas of improvement and suggestions for future works. The appendix (@sec-appendix) includes a link to a dashboard that was created with interactive versions of the graphs in this paper, additional tables, notes on reproducing and code styling, model diagnostics and validation, our idealized survey and methodology to gather data on investigators responsible for homicide cases, and our evaluation of The Washington Post's methodology.

@@

Performing root mean square error (RSME) calculations on our model in @tbl-model-result yields a RSME value of about 0.45. RSME represents the difference between the model's predicted values and observed values with 0 meaning that the predicted and observed values are the same [@citejim]. Since the model's RSME value is close to 0, we can say our model is able to predict values with less error compared to other models that have a higher RSME value.
